Inflated false-negative rates in pooled RT-PCR tests of SARS-CoV-2

### 2021-03-09 comment.tex
ama bst
many more refs

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{marginnote}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=red,linkcolor=red,bookmarks=true]{hyperref}
%strikethrough
\usepackage{soul}
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
\usepackage{float}
\usepackage[margin=0.5in]{geometry}

@@

\affil[1]{Porter School of the Environment and Earth Sciences, The Faculty of Exact Sciences, Tel Aviv
  University\\ Tel Aviv, Israel}
\affil[2]{School of Public Health, The Faculty of Medicine, Tel Aviv University\\ Tel Aviv, Israel}
\affil[3]{The Gertner Institute for Epidemiology and Health Policy Research, Tel Hashomer, Israel}
%\email{yair.daon@gmail.com}
\date{\today}

\maketitle
%%% MAKE TITLE PAGE %%%
% \bigskip
% \bigskip
% \bigskip
% \bigskip
% \begin{itemize}
%     \item Article type: Brief report.
%     \item Corresponding author: Uri Obolski, email uriobols@tauex.tau.ac.il, Phone +972526309508
%     \item Running head: Inflated false-negative rates in pooled SARS-CoV-2 tests.
%     \item Conflict of interests: None.
%     \item Financial support: Yair Daon was supported by a
%     post-doctoral fellowship from the Tel Aviv University Center for
%     Combating Pandemics and the Raymond and Beverly Sackler Dean's
%     Post-Doctoral fellowship.
%     \item Data is presented in the manuscript itself and can be found in a paper we reference to. Calculations are simple and can be easily implemented in any programming language.
% \end{itemize}
% \end{document}

@@

For the approximation commonly used in the literature estimates the scheme false-negative rate as $1-\Se^2$ (section \ref{section:ass} and \cite{Simplistic1, Simplistic2, Kim, OptimalDorfmanPool}). A short calculation shows that this approximation implies the percentage increase in scheme false-negative rate is just $100\cdot \Se$.

@@

An approximation to our results has been previously considered: $\mi \approx 1-\Se^2 $\cite{Simplistic1, Simplistic2, Kim, OptimalDorfmanPool}. Such an approximation arises when one assumes that the probability of a false-negative is identical for the pooled and single tests. Although simplistic in nature, this approximation does capture the intuition behind our results: For Donald to be considered negative under Dorfman pooling, he has to test negative twice. In addition to this approximation only being an upper bound \cite{Simplistic2}, it does not account for the effect of infection prevalence on the false-negative rates under Dorfman pooling. Supporting the importance of this effect, such an association between prevalence and the scheme false-negative rate under Dorfman pooling has been empirically noted  \cite{DorfmanYuvalDor}.

@@

\bibliographystyle{amsplain}
\bibliography{pooling, fpfn}

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{marginnote}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=red,linkcolor=red,bookmarks=true]{hyperref}
%strikethrough
\usepackage{soul}
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
\usepackage{float}
\usepackage[margin=0.5in]{geometry}
\hypersetup{linkcolor=black,citecolor=black,urlcolor=black}

@@

\affil[1]{Porter School of the Environment and Earth Sciences, The Faculty of Exact Sciences, Tel Aviv
  University\\ Tel Aviv, Israel}
\affil[2]{School of Public Health, The Faculty of Medicine, Tel Aviv University\\ Tel Aviv, Israel}
\affil[3]{The Gertner Institute for Epidemiology and Health Policy Research, Tel Hashomer, Israel}
%\email{yair.daon@gmail.com}
\date{}

\maketitle
%%% MAKE TITLE PAGE %%%
\bigskip
\bigskip
\bigskip
\bigskip
\begin{itemize}
    \item Article type: Brief report.
    \item Corresponding author: Uri Obolski, email uriobols@tauex.tau.ac.il, Phone +972526309508
    \item Running head: Inflated false-negative rates in pooled SARS-CoV-2 tests.
    \item Conflict of interests: None.
    \item Financial support: Yair Daon was supported by a
    post-doctoral fellowship from the Tel Aviv University Center for
    Combating Pandemics and the Raymond and Beverly Sackler Dean's
    Post-Doctoral fellowship.
    \item Data is presented in the manuscript itself and can be found in a paper we reference to. Calculations are simple and can be easily implemented in any programming language.
\end{itemize}
\newpage
% \end{document}

@@

For the approximation commonly used in the literature estimates the scheme false-negative rate as $1-\Se^2$ (Section \ref{section:assumptions} and \cite{Simplistic1, Simplistic2, Kim, OptimalDorfmanPool}). A short calculation shows that this approximation implies the percentage increase in scheme false-negative rate is just $100\cdot \Se$.

@@

An approximation to our results has been previously considered: $\mi \approx 1-\Se^2 $, see \cite{Simplistic1, Simplistic2, Kim, OptimalDorfmanPool}. Such an approximation arises when one assumes that the probability of a false-negative is identical for the pooled and single tests. Although simplistic in nature, this approximation does capture the intuition behind our results: For Donald to be considered negative under Dorfman pooling, he has to test negative twice. In addition to this approximation only being an upper bound \cite{Simplistic2}, it does not account for the effect of infection prevalence on the false-negative rates under Dorfman pooling. Supporting the importance of this effect, such an association between prevalence and the scheme false-negative rate under Dorfman pooling has been empirically noted  \cite{DorfmanYuvalDor}.

@@

\bibliographystyle{ama}
\bibliography{refs}
